Preventing Runtime Errors of Redis at Compile Time

### 2015-11-21 paper.tex
submitted

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
newtype Popcorn p q a = Popcorn { unPopcorn :: Redis a }

@@

The first and second argument of type \mintinline{haskell}{Popcorn} is where the
dictionaries going to stay.

To execute a \mintinline{haskell}{Popcorn} program, simply apply it to
 \mintinline{haskell}{unPopcorn} to get an ordinary program of type
 \mintinline{haskell}{Redis}, with type information erased.

@@

In Redis, \mintinline{text}{PING} does nothing but replies with
 \mintinline{text}{PONG} if the connection is alive. In Hedis,
 \mintinline{text}{PING} has type:

@@

Now we have \mintinline{haskell}{Popcorn}, let's make our own version of
\mintinline{haskell}{ping}\footnotemark

@@

The dictionary \mintinline{haskell}{xs} in the type remains unaffected after the
 action, because \mintinline{haskell}{ping} does not affect any key-value
 bindings. To encode other commands that modifies key-value bindings, we need
 type-level functions to annotate those effects on the dictionary.

@@

Commands such as \mintinline{text}{INCR} and \mintinline{text}{INCRBYFLOAT}, are
 not only container-specific, they also have some requirements on what types of
 value they could operate on.

@@

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
incr :: (KnownSymbol s, Get xs s ~ Just (StringOf Integer))
     => Proxy s -> Popcorn xs xs (Either Reply Integer)
incr key = Popcorn $ Hedis.incr (encodeKey key)

>>>>

\begin{minted}[xleftmargin=1em]{haskell}
newtype Popcorn p q a =
    Popcorn { unPopcorn :: Redis a }

@@

The first and second argument of type \mintinline{haskell}{Popcorn} is where the
dictionaries going to be.

To execute a \mintinline{haskell}{Popcorn} program, simply apply it to
 \mintinline{haskell}{unPopcorn} to get an ordinary Hedis program back,
 with type information erased.

@@

In Redis, \mintinline{text}{PING} does nothing but replies with
 \mintinline{text}{PONG} if the connection is alive. In Hedis,
 \mintinline{haskell}{ping} has type:

@@

Now with \mintinline{haskell}{Popcorn}, we could make our own version of
\mintinline{haskell}{ping}\footnotemark

@@

The dictionary \mintinline{haskell}{xs} in the type remains unaffected after the
 action, because \mintinline{haskell}{ping} does not affect any key-type
 bindings. To encode other commands that modifies key-type bindings, we need
 type-level functions to annotate those effects on the dictionary.

@@

Commands such as \mintinline{text}{INCR} and \mintinline{text}{INCRBYFLOAT}, are
 not only container-specific, they also have some requirements on what types of
 value they could operate with.

@@

\begin{minted}[xleftmargin=1em]{haskell}
incr :: (KnownSymbol s
      , Get xs s ~ Just (StringOf Integer))
     => Proxy s
     -> Popcorn xs xs (Either Reply Integer)
incr key = Popcorn $ Hedis.incr (encodeKey key)
